Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2015-05-28 cordillera-cycle.tex
Update acknowledgements.

Ice-shelve calving is computed by a double criterion. First, a
physically-realistic calving flux is computed based on eigenvalues of the
horizontal strain rate tensor \citep{Winkelmann.etal.2011,
Levermann.etal.2012}. This allows outlet glaciers to advance in confined
embayments, but prevents extensive ice-shelves to build-up in the open ocean.
Second, floating ice thinner than 50\,m is systematically calved off. A subgrid
scheme \citep{Albrecht.etal.2011} allows for a continuous migration of the
calving frontm. Such treatment of calving was applied to the Antarctic ice
sheet and shown to produce realistic calving front positons for many of the
ice-shelves \citep{Martin.etal.2011}.

@@

% Acknowledgements
\begin{acknowledgements}
We are very thankful to Constantine Khroulev, Ed Bueler and Andy Aschwanden for
providing constant help and development on PISM. This work was supported by the
Swedish Research Council~(VR) grant no. 2008-3449 to A.~P.~Stroeven, by the
German Academic Exchange Service~(DAAD) grant no.~50015537 and a Knut and Alice
Wallenberg Foundation grant to J.~Seguinot.
Computer resources were provided by the Swedish National
Infrastructure for Computing (SNIC) allocation no. 2013/1-159 to A.~P.~Stroeven
at the National Supercomputing Center (NSC).
\end{acknowledgements}

>>>>

Ice-shelve calving is computed by a double criterion. First, a
physically-realistic calving flux is computed based on eigenvalues of the
horizontal strain rate tensor \citep{Winkelmann.etal.2011,
Levermann.etal.2012}. This allows outlet glaciers to advance in confined
embayments, but prevents extensive ice-shelves to build-up in the open ocean.
Second, floating ice thinner than 50\,m is systematically calved off. A subgrid
scheme \citep{Albrecht.etal.2011} allows for a continuous migration of the
calving front. Such treatment of calving was applied to the Antarctic ice
sheet and shown to produce realistic calving front positons for many of the
ice-shelves \citep{Martin.etal.2011}.

@@

% Acknowledgements
\begin{acknowledgements}
Foremost, we would like to thank Shawn Marshall for providing a detailed,
constructive analysis of this study during J.~Seguinot's Ph.D. defence
(September 2014). His comments were used to improve the model set-up.
We are very thankful to Constantine Khroulev, Ed Bueler and Andy Aschwanden for
providing constant help and development on PISM. This work was supported by the
Swedish Research Council~(VR) grant no.~2008-3449 to A.~P.~Stroeven and by the
German Academic Exchange Service~(DAAD) grant no.~50015537 and a Knut and Alice
Wallenberg Foundation grant to J.~Seguinot. Computer resources were provided
by the Swedish National Infrastructure for Computing (SNIC) allocation
no.~2013/1-159 and~2014/1-159 to A.~P.~Stroeven at the National Supercomputing
Center (NSC).
\end{acknowledgements}
